`r params$doc_title`

### 2022-12-23 scripts/MSc.Rmd
renaming figures, preparing report

# 4. Exclude the IV if Pval > genome-wide significance threshold  (5 × 10−8) --> updated to 5 × 10−6
pvals_df %>% 
  summarize(across(.cols = everything(), function(x) sum(x < 5*10^(-6)))) %>% 
  t() %>% 
  kable(caption = "Count of significant SNPs depending on sample size")

@@

ggplot(data = my_data_harm, 
       mapping = aes(x=explained_variance_BMI*100, y= -log10(p.value.bmi),  
                    col=fto_col_annot, label=gene_label)
       )+
  geom_point(alpha=0.6)+
  ggrepel::geom_text_repel(show.legend = FALSE)+
  xlab("Explained variance in BMI in %")+
  ylab("-log10 P-val")+
  labs(title = "Explained variance exposure",
       col='SNP'
       ) +
  theme_few()+
  scale_colour_few() -> fig00
fig00

@@

filenamefig00_a <- paste0("../output/plots/", Sys.Date(), "_figure00_a.png")
ggsave(filename = filenamefig00_a, plot = fig00, 
       width = 10, height = 6, 
       units = "in"  # default
       )

filenamefig00_b <- paste0("../output/plots/", Sys.Date(), "_figure00_b.png")
ggsave(filename = filenamefig00_b, plot = fig00_b, 
       width = 10, height = 6, 
       units = "in"  # default
       )
```

@@

fig01.update
# scale_color_manual(name = "Y series", values = c("Y1" = "darkblue", "Y2" = "red"))

@@

# SAVE
filenamefig01_a <- paste0("../output/plots/", Sys.Date(), "_figure01_a.png")
filenamefig01_b <- paste0("../output/plots/", Sys.Date(), "_figure01_b.png")
ggsave(filename = filenamefig01_a, plot = fig01.update, 
       width = 10, height = 6, 
       units = "in"  # default
       )

@@

ggplot(data = plot_data_2, aes(x=maf.bmi, y=abs(beta.bmi)))+
  geom_point(alpha=0.6)+
  geom_hline(yintercept=median(abs(plot_data_2$beta.bmi)), 
             col=ggthemes_data$few$colors$Dark[6,2][[1]], alpha=0.6, linetype=2)+
  geom_vline(xintercept=median(plot_data_2$maf.bmi), 
             col=ggthemes_data$few$colors$Dark[6,2][[1]], alpha=0.6, linetype=2)+
  annotate(geom = "text", x = 0.15, y = 0.045, 
           label="relatively rare\nrelatively strong", 
           color= ggthemes_data$few$colors$Dark[2,2][[1]]
             )+
  annotate(geom = "text", x = 0.42, y = 0.05, 
           label="relatively common\nrelatively strong", 
           color=ggthemes_data$few$colors$Dark[3,2][[1]])+
  annotate(geom = "text", x = 0.1, y = 0.015, 
           label="relatively rare\nrelatively weak", color=ggthemes_data$few$colors$Dark[4,2][[1]])+
  annotate("segment", x=0.44,xend=0.42,y=0.025,yend=0.013,arrow=arrow(), 
           color=ggthemes_data$few$colors$Dark[5,2][[1]])+
  annotate(geom = "text", x = 0.44, y = 0.03, 
           label="relatively common\nrelatively weak", 
           color=ggthemes_data$few$colors$Dark[5,2][[1]])+
  #geom_text(x=0.1, y=0.05, label="hello", family = "Times New Roman",
  #          size=6, col="red")+
  xlab("Minor allele frequency")+
  ylab("Exposure effect size")+  # abs(beta_BMI)
  labs(title = "Figure 2-update",
       subtitle = "Define different genetic architectures",
       #col='', 
       #caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       ) +
  theme_few()+
  scale_colour_few() -> fig02.update
fig02.update

@@

  N_annotation <- c(10000, 100000, 200000, 300000)
  ## plot
  plotsubtitle <- paste0("relatively ", maf ,", relatively ", effect_size)
  ggplot(plot_data1, aes(x=n, y=value, col=name))+
    geom_point(alpha=0.6)+
    geom_line(alpha=0.6)+
    geom_line(aes(x=n, y=count_IVs_scaled, col="Number of IVs"), linetype="dotdash")+
    scale_x_continuous(name = paste0("Size of sample ", as.roman(1)),  # 2-sample-MR or label "Study Size"
                       labels = comma, 
                       breaks = N_annotation, #c( 10000, n[7:length(n)]),
                       limits = c(10000, 300000))+
    #ylab("% variance explained by IVs")+
    labs(title = "Figure 1", subtitle = plotsubtitle,
         col='', 
         caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits   explained by the IVs"
         ) +
    scale_y_continuous(
      # Features of the first axis
      name = "% variance explained by IVs",
      # Add a second axis and specify its features
      sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
      limits = c(0,2)
    ) + 
    theme_few()+
    #scale_colour_few() +
    #scale_color_manual(name = "", values = c("% var(U)" = "red", 
    #                                         "% var(X)" = "blue", 
    #                                         "% var(Y)" = "darkblue", 
    #                                         "Number of IVs" = "black"
    #                                         ))
    #
    scale_color_manual(name = "", values = c("% var(U)" = ggthemes_data$few$colors$Dark[2,2][[1]], 
                                             "% var(X)" = ggthemes_data$few$colors$Dark[3,2][[1]], 
                                             "% var(Y)" = ggthemes_data$few$colors$Dark[4,2][[1]], 
                                             "Number of IVs" = "black"),
                       # order
                       breaks = c( "Number of IVs", "% var(X)", "% var(Y)", "% var(U)")
    ) -> figure01.quadrant
  print(figure01.quadrant)

@@

```{r fig.height=10, fig.width=14, warning=FALSE}
fig01b.update + 
  labs(title= "", caption = "") -> fig01b.update.arrange

@@

final_plot1.arrange
final_plot1.arrange2

filename_final_plot1 <- paste0("../output/plots/", Sys.Date(), "_final_plot1.arrange.png")
filename_final_plot1b <- paste0("../output/plots/", Sys.Date(), "_final_plot1b.arrange.png")

@@

```{r forestplot-MendelianRandomization-GSD, fig.width=5, fig.height=24, warning=FALSE}
p2.gsd <- mr_forest(
  mr.obj,
  alpha = 0.05,
  snp_estimates = TRUE,
  methods = "ivw",
  ordered = TRUE
) +
  ggthemes::theme_few()

#SAVE
filename.mr.forest.gsd <- paste0("../output/plots/", Sys.Date(), "_figure_mrforest_gsd.png")
ggsave(filename = filename.mr.forest.gsd, plot = p2.gsd, 
       width = 5, 
       height = 24, 
         #units = "in"  # default
         )
```

@@

```{r funnel-plot-GSD, fig.height=3, fig.width=5}
p4.gsd <- mr_funnel(mr.obj, CI=TRUE)+
  ggthemes::theme_few()

@@

# plot
p4.gsd

@@

```{r forestplot-TwoSampleMR, fig.width=5, fig.height=24, warning=FALSE}
res_single <- TwoSampleMR::mr_singlesnp(harmonised_dat4TwoSampleMR, all_method = c("mr_egger_regression", "mr_ivw"))
p2 <- mr_forest_plot(res_single,  exponentiate = FALSE)
p2[[1]]

#SAVE
filename.mr.forest <- paste0("../output/plots/", Sys.Date(), "_figure_mrforest.png")
ggsave(filename = filename.mr.forest, plot = p2[[1]], 
       width = 5, 
       height = 24, 
         #units = "in"  # default
         )
```

@@

## plot
ggplot(plot_data1b, aes(x=n, y=value, col=name))+    # plot_data1b from section Simlating on empirical data (PVE)
  geom_point(alpha=0.6)+
  geom_line(alpha=0.6)+
  geom_line(aes(x=n, y=count_IVs_scaled, col="Number of IVs"), linetype="dotdash")+
  scale_x_continuous(name = paste0("Size of sample ", as.roman(1)),  # 2-sample-MR or label "Study Size"
                     labels = comma, 
                     breaks = N_annotation, #c( 10000, n[7:length(n)]),
                     limits = c(10000, 300000))+
  #ylab("% variance explained by IVs")+
  labs(title = "PVE with simulation added",
       col='', 
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       ) +
  scale_y_continuous(
    # Features of the first axis
    name = "% variance explained by IVs",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
    limits = c(0,10)
  ) + 
  #geom_boxplot(data=boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, group=sample_size_filtered))
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2)+
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_U*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[2,2][[1]],
               alpha=0.2, size=0.2)+
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_Y*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[4,2][[1]],
               alpha=0.2, size=0.2)+
  theme_few()+
  #scale_colour_few() +
  #scale_color_manual(name = "", values = c("% var(U)" = "red", 
  #                                         "% var(X)" = "blue", 
  #                                         "% var(Y)" = "darkblue", 
  #                                         "Number of IVs" = "black"
  #                                         ))
  #
  scale_color_manual(name = "", values = c("% var(U)" = ggthemes_data$few$colors$Dark[2,2][[1]], 
                                           "% var(X)" = ggthemes_data$few$colors$Dark[3,2][[1]], 
                                           "% var(Y)" = ggthemes_data$few$colors$Dark[4,2][[1]], 
                                           "Number of IVs" = "black"),
                     # order
                     breaks = c( "Number of IVs", "% var(X)", "% var(Y)", "% var(U)")
  ) -> plot_pve_simulated
plot_pve_simulated

@@

    limits = c(0,10)

@@

## Performance Metrics BIAS, MSE, MEAN, EMP_SE

@@

## Performance Metrics COVERAGE, COVERAGE-BIAS-ELIMINATED, TYPE1ERROR

@@

```{r add-additional-metrics-to-df}
## GSD
IVW_GSD_performance_metrics <- IVW_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(IVW_GSD_coverage_calc, IVW_GSD_coverage_bias_eliminated_calc, IVW_GSD_type1error_calc)) %>% 
  rename(coverage = IVW_GSD_coverage_calc, 
         coverage_bias_eliminated = IVW_GSD_coverage_bias_eliminated_calc, 
         type1error = IVW_GSD_type1error_calc) %>% 
  as_tibble()
MODE_GSD_performance_metrics <- MODE_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(MODE_GSD_coverage_calc, MODE_GSD_coverage_bias_eliminated_calc, MODE_GSD_type1error_calc)) %>% 
  rename(coverage = MODE_GSD_coverage_calc, 
         coverage_bias_eliminated = MODE_GSD_coverage_bias_eliminated_calc, 
         type1error = MODE_GSD_type1error_calc) %>% 
  as_tibble()
CONMIX_GSD_performance_metrics <- CONMIX_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(CONMIX_GSD_coverage_calc, CONMIX_GSD_coverage_bias_eliminated_calc, CONMIX_GSD_type1error_calc)) %>% 
  rename(coverage = CONMIX_GSD_coverage_calc, 
         coverage_bias_eliminated = CONMIX_GSD_coverage_bias_eliminated_calc, 
         type1error = CONMIX_GSD_type1error_calc) %>% 
  as_tibble()

## GBC
IVW_GBC_performance_metrics <- IVW_GBC_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(IVW_GBC_coverage_calc, IVW_GBC_coverage_bias_eliminated_calc, IVW_GBC_type1error_calc)) %>% 
  rename(coverage = IVW_GBC_coverage_calc, 
         coverage_bias_eliminated = IVW_GBC_coverage_bias_eliminated_calc, 
         type1error = IVW_GBC_type1error_calc) %>% 
  as_tibble()
MODE_GBC_performance_metrics <- MODE_GBC_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(MODE_GBC_coverage_calc, MODE_GBC_coverage_bias_eliminated_calc, MODE_GBC_type1error_calc)) %>% 
  rename(coverage = MODE_GBC_coverage_calc, 
         coverage_bias_eliminated = MODE_GBC_coverage_bias_eliminated_calc, 
         type1error = MODE_GBC_type1error_calc) %>% 
  as_tibble()
CONMIX_GBC_performance_metrics <- CONMIX_GBC_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(CONMIX_GBC_coverage_calc, CONMIX_GBC_coverage_bias_eliminated_calc, CONMIX_GBC_type1error_calc)) %>% 
  rename(coverage = CONMIX_GBC_coverage_calc, 
         coverage_bias_eliminated = CONMIX_GBC_coverage_bias_eliminated_calc, 
         type1error = CONMIX_GBC_type1error_calc) %>% 
  as_tibble()
```

@@

```{r plot-performance-metrics-bias-mse-GSD, fig.height=10, fig.width=5}
## IVW
#BIAS
ggplot(IVW_GSD_performance_metrics, aes(x=N, y=bias))+ 
  geom_point()+
  geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(-1.5,1.5))+
  xlab("Size of Sample I")+
  ylab("Bias")+
  labs(title = "IVW estimate: BMI -> GSD")+
  theme_few() -> biasplot_IVW_GSD
#MSE
ggplot(IVW_GSD_performance_metrics, aes(x=N, y=mse))+ 
  geom_point()+
  geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(0,1.8))+
  xlab("Size of Sample I")+
  ylab("MSE")+
  labs(title = "IVW estimate: BMI -> GSD")+
  theme_few() -> mseplot_IVW_GSD
ggarrange(biasplot_IVW_GSD, mseplot_IVW_GSD) -> bias_mse_plot_IVW_GSD

@@

```{r plot-performance-metrics-bias-mse-GBC, fig.height=10, fig.width=5}
## IVW
#BIAS
ggplot(IVW_GBC_performance_metrics, aes(x=N, y=bias))+ 
  geom_point()+
  geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(-1.5,1.5))+
  xlab("Size of Sample I")+
  ylab("Bias")+
  labs(title = "IVW estimate: BMI -> GBC")+
  theme_few() -> biasplot_IVW_GBC
#MSE
ggplot(IVW_GBC_performance_metrics, aes(x=N, y=mse))+ 
  geom_point()+
    geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_y_continuous(limits = c(0,1.8))+
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("MSE")+
  labs(title = "IVW estimate: BMI -> GBC")+
  theme_few() -> mseplot_IVW_GBC
ggarrange(biasplot_IVW_GBC, mseplot_IVW_GBC) -> bias_mse_plot_IVW_GBC

>>>>

# 4. Exclude the IV if Pval > genome-wide significance threshold  (5 × 10−8) --> updated to 5 × 10−6
pvals_df %>% 
  summarize(across(.cols = everything(), function(x) sum(x < 5*10^(-6)))) %>% 
  t() %>% 
  cbind(n) %>% 
  base::as.data.frame() %>% 
  tibble::rownames_to_column() %>% 
  rename(sample_size = n, No_of_IVs=V1) %>% 
  select(sample_size, No_of_IVs) %>% 
  kable(caption = "Count of significant SNPs depending on sample size") %>% 
  kable_styling(font_size=10)

@@

ggplot(data = my_data_harm, 
       mapping = aes(x=explained_variance_BMI*100, y= -log10(p.value.bmi),  
                    col=fto_col_annot, label=gene_label)
       )+
  geom_point(alpha=0.6)+
  ggrepel::geom_text_repel(show.legend = FALSE)+
  xlab("Explained variance in BMI in %")+
  ylab("-log10 P-val")+
  labs(title = "Explained variance exposure",
       col='SNP'
       ) +
  theme_few()+
  scale_colour_few() -> fig00
# fig00   # we use the sample size dependent formula

@@

filenamefig00_a <- paste0("../output/plots/", Sys.Date(), "_explained_var_X_old_formula.png")
ggsave(filename = filenamefig00_a, plot = fig00, 
       width = 10, height = 6, 
       units = "in"  # default
       )

filenamefig00_b <- paste0("../output/plots/", Sys.Date(), "_explained_var_X_new_sample_size_dep.png")
ggsave(filename = filenamefig00_b, plot = fig00_b, 
       width = 10, height = 6, 
       units = "in"  # default
       )
```

@@

# fig01.update   # old formula for PVE exposure X (without sample size adjusting)
# 
# scale_color_manual(name = "Y series", values = c("Y1" = "darkblue", "Y2" = "red"))

@@

# SAVE
filenamefig01_a <- paste0("../output/plots/", Sys.Date(), "_figure01_old_PVE_X_formula.png")
filenamefig01_b <- paste0("../output/plots/", Sys.Date(), "_figure01_new_PVE_X_formula.png")
ggsave(filename = filenamefig01_a, plot = fig01.update, 
       width = 10, height = 6, 
       units = "in"  # default
       )

@@

ggplot(data = plot_data_2, aes(x=maf.bmi, y=abs(beta.bmi)))+
  geom_point(alpha=0.6)+
  geom_hline(yintercept=median(abs(plot_data_2$beta.bmi)), 
             col=ggthemes_data$few$colors$Dark[6,2][[1]], alpha=0.6, linetype=2)+
  geom_vline(xintercept=median(plot_data_2$maf.bmi), 
             col=ggthemes_data$few$colors$Dark[6,2][[1]], alpha=0.6, linetype=2)+
  annotate(geom = "text", x = 0.15, y = 0.045, 
           label="relatively rare\nrelatively strong", 
           color= ggthemes_data$few$colors$Dark[2,2][[1]]
             )+
  annotate(geom = "text", x = 0.42, y = 0.05, 
           label="relatively common\nrelatively strong", 
           color=ggthemes_data$few$colors$Dark[3,2][[1]])+
  annotate(geom = "text", x = 0.1, y = 0.015, 
           label="relatively rare\nrelatively weak", color=ggthemes_data$few$colors$Dark[4,2][[1]])+
  annotate("segment", x=0.44,xend=0.42,y=0.025,yend=0.013,arrow=arrow(), 
           color=ggthemes_data$few$colors$Dark[5,2][[1]])+
  annotate(geom = "text", x = 0.44, y = 0.03, 
           label="relatively common\nrelatively weak", 
           color=ggthemes_data$few$colors$Dark[5,2][[1]])+
  #geom_text(x=0.1, y=0.05, label="hello", family = "Times New Roman",
  #          size=6, col="red")+
  xlab("Minor allele frequency")+
  ylab("Exposure effect size")+  # abs(beta_BMI)
  labs(title = "",
       subtitle = "Define different genetic architectures",
       #col='', 
       #caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       ) +
  theme_few()+
  scale_colour_few() -> fig02.update
fig02.update

@@

  N_annotation <- c(10000, 100000, 200000, 300000)
  ## plot
  plotsubtitle <- paste0("relatively ", maf ,", relatively ", effect_size)
  ggplot(plot_data1, aes(x=n, y=value, col=name))+
    geom_point(alpha=0.6)+
    geom_line(alpha=0.6)+
    geom_line(aes(x=n, y=count_IVs_scaled, col="Number of IVs"), linetype="dotdash")+
    scale_x_continuous(name = paste0("Size of sample ", as.roman(1)),  # 2-sample-MR or label "Study Size"
                       labels = comma, 
                       breaks = N_annotation, #c( 10000, n[7:length(n)]),
                       limits = c(10000, 300000))+
    #ylab("% variance explained by IVs")+
    labs(title = "", subtitle = plotsubtitle,
         col='', 
         caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits   explained by the IVs"
         ) +
    scale_y_continuous(
      # Features of the first axis
      name = "% variance explained by IVs",
      # Add a second axis and specify its features
      sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
      limits = c(0,2)
    ) + 
    theme_few()+
    #scale_colour_few() +
    #scale_color_manual(name = "", values = c("% var(U)" = "red", 
    #                                         "% var(X)" = "blue", 
    #                                         "% var(Y)" = "darkblue", 
    #                                         "Number of IVs" = "black"
    #                                         ))
    #
    scale_color_manual(name = "", values = c("% var(U)" = ggthemes_data$few$colors$Dark[2,2][[1]], 
                                             "% var(X)" = ggthemes_data$few$colors$Dark[3,2][[1]], 
                                             "% var(Y)" = ggthemes_data$few$colors$Dark[4,2][[1]], 
                                             "Number of IVs" = "black"),
                       # order
                       breaks = c( "Number of IVs", "% var(X)", "% var(Y)", "% var(U)")
    ) -> figure01.quadrant
  print(figure01.quadrant)

@@

```{r FINAL-PLOT-1-huray, fig.height=10, fig.width=14, message=FALSE, warning=FALSE}
fig01b.update + 
  labs(title= "", caption = "") -> fig01b.update.arrange

@@

# final_plot1.arrange   # OLD
final_plot1.arrange2   # use this!

filename_final_plot1 <- paste0("../output/plots/", Sys.Date(), "_final_plot1.arrange_OLD.png")
filename_final_plot1b <- paste0("../output/plots/", Sys.Date(), "_final_plot1b.arrange_NEW.png")

@@

```{r forestplot-MendelianRandomization-GSD, fig.width=5, fig.height=27, warning=FALSE}
p2.gsd <- mr_forest(
  mr.obj,
  alpha = 0.05,
  snp_estimates = TRUE,
  methods = "ivw",
  ordered = TRUE
) +
  ggthemes::theme_few()

#SAVE
filename.mr.forest.gsd <- paste0("../output/plots/", Sys.Date(), "_figure_mrforest_GSD.png")
ggsave(filename = filename.mr.forest.gsd, plot = p2.gsd, 
       width = 5, 
       height = 24, 
         #units = "in"  # default
         )
```

@@

```{r funnel-plot-GSD, fig.height=3, fig.width=5}
p4.gsd <- mr_funnel(mr.obj, CI=TRUE)

@@

# plot
p4.gsd <- p4.gsd+
  ggthemes::theme_few()
p4.gsd

@@

```{r forestplot-TwoSampleMR-GBC, fig.width=5, fig.height=24, warning=FALSE}
res_single <- TwoSampleMR::mr_singlesnp(harmonised_dat4TwoSampleMR, all_method = c("mr_egger_regression", "mr_ivw"))
p2 <- mr_forest_plot(res_single,  exponentiate = FALSE)
p2[[1]]

#SAVE
filename.mr.forest <- paste0("../output/plots/", Sys.Date(), "_figure_mrforest_GBC.png")
ggsave(filename = filename.mr.forest, plot = p2[[1]], 
       width = 5, 
       height = 24, 
         #units = "in"  # default
         )
```

@@

## plot
ggplot(plot_data1b, aes(x=n, y=value, col=name))+    # plot_data1b from section Simlating on empirical data (PVE)
  geom_point(alpha=0.6)+
  geom_line(alpha=0.6)+
  geom_line(aes(x=n, y=count_IVs_scaled, col="Number of IVs"), linetype="dotdash")+
  scale_x_continuous(name = paste0("Size of sample ", as.roman(1)),  # 2-sample-MR or label "Study Size"
                     labels = comma, 
                     breaks = N_annotation, #c( 10000, n[7:length(n)]),
                     limits = c(10000, 300000))+
  #ylab("% variance explained by IVs")+
  labs(title = "PVE with simulation added",
       col='', 
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       ) +
  scale_y_continuous(
    # Features of the first axis
    name = "% variance explained by IVs",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
    limits = c(0,7.5)
  ) + 
  #geom_boxplot(data=boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, group=sample_size_filtered))
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2)+
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_U*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[2,2][[1]],
               alpha=0.2, size=0.2)+
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_Y*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[4,2][[1]],
               alpha=0.2, size=0.2)+
  theme_few()+
  #scale_colour_few() +
  #scale_color_manual(name = "", values = c("% var(U)" = "red", 
  #                                         "% var(X)" = "blue", 
  #                                         "% var(Y)" = "darkblue", 
  #                                         "Number of IVs" = "black"
  #                                         ))
  #
  scale_color_manual(name = "", values = c("% var(U)" = ggthemes_data$few$colors$Dark[2,2][[1]], 
                                           "% var(X)" = ggthemes_data$few$colors$Dark[3,2][[1]], 
                                           "% var(Y)" = ggthemes_data$few$colors$Dark[4,2][[1]], 
                                           "Number of IVs" = "black"),
                     # order
                     breaks = c( "Number of IVs", "% var(X)", "% var(Y)", "% var(U)")
  ) -> plot_pve_simulated
#plot_pve_simulated

@@

    limits = c(0,7.5)

@@

## Performance Metrics

### Calculate BIAS, MSE, MEAN, EMP_SE

@@

### Calculate COVERAGE, COVERAGE-BIAS-ELIMINATED, TYPE1ERROR

@@

### GSD Performance Metrics

```{r add-additional-metrics-to-df-and-print-GSD}
## GSD --------------------------
IVW_GSD_performance_metrics <- IVW_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(IVW_GSD_coverage_calc, IVW_GSD_coverage_bias_eliminated_calc, IVW_GSD_type1error_calc)) %>% 
  rename(coverage = IVW_GSD_coverage_calc, 
         coverage_bias_eliminated = IVW_GSD_coverage_bias_eliminated_calc, 
         type1error = IVW_GSD_type1error_calc) %>% 
  as_tibble()
IVW_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "IVW method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)

MODE_GSD_performance_metrics <- MODE_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(MODE_GSD_coverage_calc, 
                   MODE_GSD_coverage_bias_eliminated_calc, MODE_GSD_type1error_calc)) %>% 
  rename(coverage = MODE_GSD_coverage_calc, 
         coverage_bias_eliminated = MODE_GSD_coverage_bias_eliminated_calc, 
         type1error = MODE_GSD_type1error_calc) %>% 
  as_tibble()

MODE_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "MODE method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)

CONMIX_GSD_performance_metrics <- CONMIX_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(CONMIX_GSD_coverage_calc, 
                   CONMIX_GSD_coverage_bias_eliminated_calc, CONMIX_GSD_type1error_calc)) %>% 
  rename(coverage = CONMIX_GSD_coverage_calc, 
         coverage_bias_eliminated = CONMIX_GSD_coverage_bias_eliminated_calc, 
         type1error = CONMIX_GSD_type1error_calc) %>% 
  as_tibble()
CONMIX_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "CONMIX method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
```

### GBC Performance Metrics

```{r add-additional-metrics-to-df-and-print-GBC}
## GBC --------------------------
IVW_GBC_performance_metrics <- IVW_GBC_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(IVW_GBC_coverage_calc, 
                   IVW_GBC_coverage_bias_eliminated_calc, IVW_GBC_type1error_calc)) %>% 
  rename(coverage = IVW_GBC_coverage_calc, 
         coverage_bias_eliminated = IVW_GBC_coverage_bias_eliminated_calc, 
         type1error = IVW_GBC_type1error_calc) %>% 
  as_tibble()
IVW_GBC_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "IVW method on BMI -> GBC performance metrics") %>% 
  kable_styling(font_size=10)

MODE_GBC_performance_metrics <- MODE_GBC_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(MODE_GBC_coverage_calc, 
                   MODE_GBC_coverage_bias_eliminated_calc, MODE_GBC_type1error_calc)) %>% 
  rename(coverage = MODE_GBC_coverage_calc, 
         coverage_bias_eliminated = MODE_GBC_coverage_bias_eliminated_calc, 
         type1error = MODE_GBC_type1error_calc) %>% 
  as_tibble()
MODE_GBC_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "MODE method on BMI -> GBC performance metrics") %>% 
  kable_styling(font_size=10)
CONMIX_GBC_performance_metrics <- CONMIX_GBC_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(CONMIX_GBC_coverage_calc, 
                   CONMIX_GBC_coverage_bias_eliminated_calc, CONMIX_GBC_type1error_calc)) %>% 
  rename(coverage = CONMIX_GBC_coverage_calc, 
         coverage_bias_eliminated = CONMIX_GBC_coverage_bias_eliminated_calc, 
         type1error = CONMIX_GBC_type1error_calc) %>% 
  as_tibble()
CONMIX_GBC_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "CONMIX method on BMI -> GBC performance metrics") %>% 
  kable_styling(font_size=10)
```

@@

```{r plot-performance-metrics-bias-mse-GSD, fig.height=10, fig.width=8}
## IVW
#BIAS
ggplot(IVW_GSD_performance_metrics, aes(x=N, y=bias))+ 
  geom_point()+
  geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(-1.5,1.5))+
  xlab("Size of Sample I")+
  ylab("Bias")+
  labs(title = "IVW estimate: BMI -> GSD")+
  theme_few() -> biasplot_IVW_GSD
#MSE
ggplot(IVW_GSD_performance_metrics, aes(x=N, y=mse))+ 
  geom_point()+
  geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(0,1.8))+
  xlab("Size of Sample I")+
  ylab("MSE")+
  labs(title = "IVW estimate: BMI -> GSD")+
  theme_few() -> mseplot_IVW_GSD
ggarrange(biasplot_IVW_GSD, mseplot_IVW_GSD) -> bias_mse_plot_IVW_GSD

@@

```{r plot-performance-metrics-bias-mse-GBC, fig.height=10, fig.width=8}
## IVW
#BIAS
ggplot(IVW_GBC_performance_metrics, aes(x=N, y=bias))+ 
  geom_point()+
  geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(-1.5,1.5))+
  xlab("Size of Sample I")+
  ylab("Bias")+
  labs(title = "IVW estimate: BMI -> GBC")+
  theme_few() -> biasplot_IVW_GBC
#MSE
ggplot(IVW_GBC_performance_metrics, aes(x=N, y=mse))+ 
  geom_point()+
    geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_y_continuous(limits = c(0,1.8))+
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("MSE")+
  labs(title = "IVW estimate: BMI -> GBC")+
  theme_few() -> mseplot_IVW_GBC
ggarrange(biasplot_IVW_GBC, mseplot_IVW_GBC) -> bias_mse_plot_IVW_GBC
